---
title: "Algemene Analyse Thesis"
output: html_notebook
---

First, load all required packages

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

Read data

```{r}
rawdata <- read.csv("data/raw/Glass eel stock deepfreeze 2017.csv", header = TRUE, sep = ";")
rawdata <- data.table(rawdata)
rawdata <- rawdata[,Tube.N.:remarks]
rawdata$Date <- dmy(rawdata$Date)
attach(rawdata)
```

Check the catch location

```{r}
plot_location <- ggplot(data=rawdata, aes(x=Location)) +
  geom_bar(width=0.2, fill='steelblue') + 
  theme_light()
plot_location
```

Check catch sizes throughout time

```{r}
plot_month <- ggplot(data=rawdata, aes(x=month(Date,label=TRUE))) +
  geom_bar(width=0.2, fill='steelblue') +
  #geom_text(aes(label=rawdata),vjust=-0.3,size=3.5) Count labels boven barplot <- lukt niet
  theme_light()
plot_month

plot_week <- ggplot(data=rawdata,aes(x=week(Date))) +
  geom_bar(width=0.2, fill='steelblue') +
  #geom_text(aes(label=rawdata),vjust=-0.3,size=3.5) Count labels boven barplot <- lukt niet
  theme_light()
plot_week
```

Check pigmentation throughout time

```{r}
plot_pigm <- ggplot(data=rawdata, aes(x=week(Date), fill=pigmentation.stage)) +
  geom_bar(position=position_dodge())
plot_pigm

plot_pigm2 <- ggplot(data=rawdata, aes(x=month(Date), fill=pigmentation.stage)) +
  geom_bar(position=position_dodge())
plot_pigm2
```


Condition Factor vs time
```{r}
plot <- qplot(x=Date, y=condition.factor, data=rawdata, geom="point")
plot
```

Length vs pigmentation stage
```{r}
plot_pigm_len <- ggplot(data = rawdata, aes(x=pigmentation.stage,y=length..mm.)) +
  geom_boxplot()
plot_pigm_len # elver outlier
```

TO DO

Weight vs time


Length vs time

