---
title: "Data exploration Thesis"
author: "Michiel Perneel"
date: "March 2019"
output:
  html_document: default
  pdf_document: default
---
# Data setup

In this section, all the required libraries are read, and the data is uploaded in r.
https://bookdown.org/yihui/rmarkdown/output-formats.html


```{r setup, include=FALSE}
#update.packages()
library(ggplot2)
library(readxl)
library(lubridate)
library(tibble)
library(ggbiplot)
library(dplyr)
library(janitor)
library(plyr)
library(anytime)
library(ggforce)
```

Now the data is loaded

```{r}
setwd("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw")
maaginhoud <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Maaginhoud.csv", sep = ";", dec = ",")) # leest de ruwe dataset (count van maaginhoud)
head(maaginhoud)
maaginhoud2 <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Maaginhoud2.csv", sep = ";", dec = ","))
head(maaginhoud2)
data_inbo <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Glass eel stock deepfreeze 2017.csv", sep = ";", dec = ",")) # leest de data van het inbo genoteerd bij de glasaalstaalname
head(data_inbo)
```

And then we can start exploring!

# Visual Exploration

## Environmental Data from INBO

```{r pressure, echo=FALSE}
barplot1 <- ggplot(data_inbo, aes(Location)) +
  geom_bar() +
  ggtitle("Location of glass eel catch")
barplot1

barplot1b <- ggplot(data_inbo, aes(Catchment.method)) +
  geom_bar() +
  ggtitle("Catchment method")
barplot1b

barplot2 <- ggplot(data_inbo, aes(month(Date))) +
  geom_bar() +
  ggtitle("Month of glass eel catch")
barplot2

barplot3 <- ggplot(data_inbo, aes(week(Date))) +
  geom_bar() +
  ggtitle("Week of glass eel catch")
barplot3

plot4 <- ggplot(data_inbo, aes(week(Date), length..mm.)) +
  geom_point() +
  ggtitle("Length of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method)
plot4

plot5 <- ggplot(data_inbo, aes(week(Date), weight.mg.)) +
  geom_point() + 
  ggtitle("Weight of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method)
plot5

plot6 <- ggplot(data_inbo, aes(week(Date), fill = pigmentation.stage)) +
  geom_bar() +
  ggtitle("Pigmentation stage of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method)
plot6

plot7 <- ggplot(data_inbo, aes(week(Date), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method)
plot7

```

## Sampling location 

At which locality are most glass eel caught?

VA_PG_LO_PA: Veurne Ambacht canal pumping station left bank eel ladder
VA_PG_RO_PA: Veurne Ambacht canal pumping station right bank eel ladder
VA_PG_LO_SU: Veurne Ambacht canal pumping station left bank substrates
VA_PG_RO_SU: Veurne Ambacht canal pumping station right bank substrates
VA_MI_LO_SU: Veurne Ambacht canal middle left bank substrates
VA_MI_RO_SU: Veurne Ambacht canal middle right bank substrates
VA_SC_LO_SU: Veurne Ambacht canal sluicecomplex Ganzepoot left bank substrates
VA_SC_RO_SU:  Veurne Ambacht canal sluicecomplex Ganzepoot right bank substrates
VA_PG_KR_NA: Veurne Ambacht canal pumpingstation liftnets night
GA_SU: Ganzepoot substrates

Onderstaande code werkt niet en is eigenlijk overbodig

```{r, echo = FALSE, eval= FALSE}
locations <- c("GA-SU", "PG-KR-NA", "SC-RO-SU", "SC-LO-SU","MI-RO-SU","MI-LO-SU", "PG-RO-SU", "PG-LO-SU", "PG-RO-PA", "PG-LO-PA")

maaginhoud.locatie <- mapvalues(maaginhoud$Locatie, from = locations, to = c("Ganzepoot", "Pompstation kruisnetten", "Sluiscomplex", "Sluiscomplex", "Midden Veurne-Ambachtkanaal", "Midden Veurne-Ambachtkanaal", "Pompgemaal", "Pompgemaal", "Pompgemaal", "Pompgemaal"))
maaginhoud$Locatie2 <- maaginhoud.locatie

barplot1 <- ggplot(maaginhoud, aes(Locatie2)) +
  geom_bar()
barplot1

#register_google(key = )
#mapImageData3 <- get_map(location = c(lon = 2.7552026, lat = 51.1346237),color = "color", source = "google", maptype = "roadmap", zoom = 16)
 
#ggmap(mapImageData3, extent = "device", ylab = "Latitude", xlab = "Longitude")
```


## Piecharts

https://www.zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/


```{r}

colnames <- c("Microplastics.Contaminatie.vezels..katoen..", "Cladocera.sp.", "Annelida", "Polychaete", "Isopoda", "Diptera.sp.", "Chironomida.sp.", "Crustaceae.sp.", "Cycloida.sp.", "Unidentified.sp.", 'Amphipoda.sp.', 'Calanoida.sp.', "Copepoda.sp.", "Harpacticoid.Copepod", "Hexapode.sp....", "keverlarve", "Pennate.diatomee","Plantae.sp.")

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud2, aes_string(x="''", y = colnames[i], fill = "Methode")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud2, aes_string(x="''", y = colnames[i], fill = "Locatie_A")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

```


But now, we want to constructs piecharts which are not absolute numbers, but relative numbers.
For example, if a glass eel ate 1 polychaete out of the total of 50 found polychaetes, this results in a relative number on the pie chart of 2%

```{r}
maaginhoud2 <- remove_empty(maaginhoud2, 'rows')
col_sum <- colSums(maaginhoud2[7:24], na.rm = TRUE)

maaginhoud3 <- maaginhoud2[1:6]
new_column <- list()

for (count in 7:length(maaginhoud2)) {
  print(count)
  new_column <- (maaginhoud2[count] / col_sum[count - 6])
  maaginhoud3 <- cbind(maaginhoud3, new_column)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud3, aes_string(x="''", y = colnames[i], fill = "Methode")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud3, aes_string(x="''", y = colnames[i], fill = "Locatie_A")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

```

Now we want to compose relative piecharts divided according to pigmentation stage

```{r}
data_inbo_pigmentation <- data_inbo[,c("nr","pigmentation.stage")]
maaginhoud4 <- left_join(maaginhoud2, data_inbo_pigmentation, by='nr')

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud4, aes_string(x="''", y = colnames[i], fill = "pigmentation.stage")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}
 
```

Now we want to compare what the relative percentage caught per method & location is
To do so, we need a transposed data table. This needs some more work

```{r, eval = FALSE, echo = FALSE}
maaginhoud5 <- select(maaginhoud2, -nr, -datum, -Locatie, -Locatie_A, -Locatie_Oever)
maaginhoud5 <- group_by(maaginhoud5, "Methode")
maaginhoud5 <- data.frame(t(maaginhoud5), header = TRUE)
names(maaginhoud5) <- maaginhoud5[1,]
maaginhoud5 <- maaginhoud5[-1,]


```

## Bargraphs

Now we want to represent this for the different food groups over the time series

```{r}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud4, aes_string(x=week(as.Date(maaginhoud4$datum)), y = colnames[i], fill = "pigmentation.stage")) +
    geom_bar(width = 1, stat="identity") +
    xlab(label = "Week of 2017")
  print(bp)
}
```

# Environmental samples

```{r}
environment2016_ind <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Individuals per liter 2016.csv", sep = ";", header = TRUE, dec = ","))

env_cyclo <- ggplot(environment2016_ind, aes(week(as.Date(Datum)), Cyclopoida)) +
  geom_point() +
  ylab("Cyclopoida ind/L 2016")
env_cyclo

env_alona_a <- ggplot(environment2016_ind, aes(week(Datum), Alona.affinis)) +
  geom_point() +
  ylab("Alona affinis ind/L 2016")
env_alona_a

env_alona_r <- ggplot(environment2016_ind, aes(week(Datum), Alona.rectangula)) +
  geom_point() +
  ylab("Alona rectangula ind/L 2016")
env_alona_r

env_chydorus <- ggplot(environment2016_ind, aes(week(Datum), Chydorus.sphaericus)) +
  geom_point() +
  ylab("Chydorus sphaericus ind/L 2016")
env_chydorus

env_daphnia <- ggplot(environment2016_ind, aes(week(Datum), Daphnia.galeata)) +
  geom_point() +
  ylab("Daphnia galeata ind/L 2016")
env_daphnia 

env_pleuroxus <- ggplot(environment2016_ind, aes(week(Datum), Pleuroxus.aduncus)) +
  geom_point() +
  ylab("Pleuroxus aduncus ind/L 2016")
env_pleuroxus
```


# Indices

Here, we calculate some indices from the dataset and visually explore these. 

## Condition Factor

First, the condition factor is analysed. Condition factor is already a variable in the dataset, calculated by the INBO

```{r}
plot_condfact_method <- ggplot(data_inbo, aes(week(Date), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method)
plot_condfact_method

plot_condfact_location <- ggplot(data_inbo, aes(week(Date), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") +
  facet_grid(.~Location)
plot_condfact_location

plot_condfact_pigm <- ggplot(data_inbo, aes(pigmentation.stage, condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") 
plot_condfact_pigm

```

## Ratio visceral organs/total body mass

Second, we calculate the ratio of visceral organs on total body mass.

```{r}
maaginhoud6 <- select(maaginhoud, nr, datum, Gewicht.Glasaal, Gewicht.maag.darmstelsel)
maaginhoud6 <- mutate(maaginhoud6, ratio_visceral_total = Gewicht.maag.darmstelsel / Gewicht.Glasaal)

plot_ratio_method <- ggplot(maaginhoud6, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") 
plot_ratio_method 

# Dikke outlier wegwerken

maaginhoud6_wo_outlier <- filter(maaginhoud6, ratio_visceral_total < 1)
plot_ratio_method <- ggplot(maaginhoud6_wo_outlier, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") 
plot_ratio_method 
```

According to previous plot, glass eel do tend to be more fed at the end of spring. This is true for all catchment methods & locations. But is this really the case?

```{r}
nr_locatie_methode <- select(maaginhoud2, nr, Locatie_A, Locatie_Oever, Methode)
nr_pigmentation_condfact <- select(data_inbo, nr, pigmentation.stage, condition.factor)
maaginhoud7 <- left_join(maaginhoud6_wo_outlier, nr_locatie_methode, by='nr')
maaginhoud7 <- left_join(maaginhoud7, nr_pigmentation_condfact, by='nr')

plot_ratio_location <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Locatie_A)
plot_ratio_location

plot_ratio_method <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Methode)
plot_ratio_method

plot_ratio_location2 <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Locatie_Oever) 
plot_ratio_location2

plot_ratio_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") 
plot_ratio_pigm_methode

plot_ratio_pigm_locatie <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Locatie_A)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") 
plot_ratio_pigm_locatie

plot_ratio_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") +
  facet_grid(.~Locatie_A)
plot_ratio_pigm_methode

maaginhoud7$datum <- strptime(as.character(maaginhoud7$datum), "%d/%m/%Y")
plot_ratio_tijd_methode <- ggplot(maaginhoud7, aes(week(datum), ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs time") +
  facet_grid(.~Locatie_A) 
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_ratio_tijd_methode


#   ANIMATED PLOTS

library(gganimate)
library(gifski)
crazyplot <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, colour = Methode)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~Locatie_A) +
  # Here comes the gganimate specific bits
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'life expectancy') +
  transition_time(week(datum)) +
  ease_aes('linear')
crazyplot
crazyplot <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, colour = Methode)) +
  geom_point() +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~Locatie_A) 
crazyplot
```

And indeed, it is the case across methods and locations.However, data from the pompgemaal is probably most reliable, since not all pigmentation stages were caught at other locations, and only substrates were used to catch glass eels.

## Fulness Index

Next, the Fulness Index is calculated.

# Species Accumulation plot & Fun with VEGAN

http://spatialecology.weebly.com/r-code--data/category/plotting

```{r}
library(vegan)
maaginhoud8 <- select(maaginhoud2, Microplastics.Contaminatie.vezels..katoen..:Plantae.sp.)

accurve<-specaccum(maaginhoud8, method="random", permutations=100)
#plot(accurve$sites, accurve$richness, xlab="Number of glass eel analysed", ylab="Species Richness")
```


# PCA

PCA as exploration of the stomach analysis data

https://www.datacamp.com/community/tutorials/pca-analysis-r


```{r}

maaginhoud2.pca <- prcomp(na.omit(maaginhoud2[7:24]), center = TRUE, scale. = TRUE)
str(maaginhoud2.pca)
ggbiplot(maaginhoud2.pca)
```
