---
title: "Analysis complete INBO dataset 2017"
author: "Michiel Perneel"
date: "18 maart 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data & Packages

```{r}
library(ggplot2)
library(readxl)
library(lubridate)
library(wesanderson)
library(tibble)
library(ggbiplot)
library(dplyr)
library(janitor)
library(plyr)
library(anytime)
library(ggforce)
library(vegan)

environment2016_ind <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Individuals per liter 2016.csv", sep = ";", header = TRUE, dec = ","))

data_inbo_161718_morfo <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/data_inbo_161718_morfo.csv", sep = ";", header = TRUE, dec = ","))
data_inbo_161718_morfo$Datum <- strptime(as.character(data_inbo_161718_morfo$Datum), "%d/%m/%Y")

data_inbo_gekuist <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/data_inbo_glasaal_gekuist.csv", sep = ";", header = TRUE, dec = ","))

maaginhoud_16 <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/data vandendriessche.csv", sep = ";", header = TRUE, dec = ","))
```

## Biometric data

In this part, we read the data from INBO to visualize how much glass eel are caught and what the annual variance is. 

```{r cars}
data_inbo_gekuist$Date <- strptime(as.character(data_inbo_gekuist$Date), "%d/%m/%Y")
data_inbo_gekuist <- mutate(data_inbo_gekuist, year = year(data_inbo_gekuist$Date))

pal <- wes_palette("Zissou1", 6, type = "continuous")
barplot1 <- ggplot( na.omit(data_inbo_gekuist), aes(week(Date), fill = ..count..)) +
  geom_bar() +
  xlab("Week") +
  ylab("Aantal gevangen glasaaltjes") +
  scale_fill_gradient(low = pal[3], high = pal[6]) +
  facet_grid(.~year) +
  theme_classic()
barplot1

data_inbo_gekuist_17 <- filter(data_inbo_gekuist, as.Date(year) ==  "2017")

geom1 <- ggplot( data_inbo_gekuist, aes(x = week(Date), y = Condition_factor)) +
  geom_point() +
  geom_smooth() +
  xlab("Week of year") +
  ylab("Condition factor of glass eel caught") +
  ggtitle("Week of glass eel catch") +
  scale_fill_gradient(low = pal[3], high = pal[6]) +
  facet_grid(Location_type~year) +
  theme_classic()
geom1

```

Now we visualize how their condition factor changes over time.

## Exploration of 2016 data

```{r}
environment2016_ind <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Individuals per liter 2016.csv", sep = ";", header = TRUE, dec = ","))

env_cyclo <- ggplot(environment2016_ind, aes(week(as.Date(Datum)), Cyclopoida)) +
  geom_point() +
  ylab("Cyclopoida ind/L 2016")
env_cyclo

env_alona_a <- ggplot(environment2016_ind, aes(week(Datum), Alona.affinis)) +
  geom_point() +
  ylab("Alona affinis ind/L 2016")
env_alona_a

env_alona_r <- ggplot(environment2016_ind, aes(week(Datum), Alona.rectangula)) +
  geom_point() +
  ylab("Alona rectangula ind/L 2016")
env_alona_r

env_chydorus <- ggplot(environment2016_ind, aes(week(Datum), Chydorus.sphaericus)) +
  geom_point() +
  ylab("Chydorus sphaericus ind/L 2016")
env_chydorus

env_daphnia <- ggplot(environment2016_ind, aes(week(Datum), Daphnia.galeata)) +
  geom_point() +
  ylab("Daphnia galeata ind/L 2016")
env_daphnia 

env_pleuroxus <- ggplot(environment2016_ind, aes(week(Datum), Pleuroxus.aduncus)) +
  geom_point() +
  ylab("Pleuroxus aduncus ind/L 2016")
env_pleuroxus

row_sum <- rowSums(maaginhoud_16[3:16], na.rm = TRUE)

maaginhoud_rel16 <- maaginhoud_16[1:2]
new_row <- list()

for (count in length(maaginhoud_16$Date.week)) {
  new_row <- (maaginhoud_16[count,3:16] / row_sum[count])
  new_row <- insert(new_row, ats = c(0, 1), values = maaginhoud_rel16[count, 1:2])
  maaginhoud_rel16 <- rbind(maaginhoud_rel16, new_row)
}

```

## Feeding Preference

Together with the data from Charlottes' bachelor dissertation, feeding preference in 2016 is checked.

```{r pressure, echo=FALSE}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
