---
title: "Data exploration Thesis"
subtitle: "Version 1"
author: "Michiel Perneel"
date: "March 2019"
output:
  html_document
---
# Data setup

In this section, all the required libraries are read, and the data is uploaded in r.
https://bookdown.org/yihui/rmarkdown/output-formats.html


```{r setup, include=FALSE}
#update.packages()
library(ggplot2)
library(readxl)
library(lubridate)
library(wesanderson)
library(tibble)
library(ggbiplot)
library(dplyr)
library(janitor)
library(plyr)
library(anytime)
library(ggforce)
```

Now the data is loaded

```{r}
setwd("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw")
maaginhoud <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Maaginhoud.csv", sep = ";", dec = ",")) # leest de ruwe dataset (count van maaginhoud)
head(maaginhoud)
maaginhoud2 <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Maaginhoud2.csv", sep = ";", dec = ","))
head(maaginhoud2)
data_inbo <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Glass eel stock deepfreeze 2017.csv", sep = ";", dec = ","))
# leest de data van het inbo genoteerd bij de glasaalstaalname
head(data_inbo)
data_inbo$Date <- strptime(as.character(data_inbo$Date), "%d/%m/%Y")

```

And then we can start exploring!

# Visual Exploration

## Environmental Data from INBO

```{r pressure, echo=FALSE}
# Setting the sampling locations in the correct order
data_inbo$Location <- factor(data_inbo$Location, levels = c("GA_SU", "VA_SC_LO_SU", "VA_SC_RO_SU", "VA_MI_RO_SU", "VA_PG_LO_SU", "VA_PG_RO_SU", "VA_PG_LO_PA", "VA_PG_RO_PA", "VA_PG_KR_NA"))

#data_inbo$Location <- revalue(data_inbo$Location, c("GA_SU"="Ganzepoot Substraat", "VA_SC_LO_SU"="Veurne-Ambacht SC Linkeroever Substraat", "VA_SC_RO_SU"="Veurne-Ambact SC Rechteroever Substraat", "VA_MI_RO_SU"="Veurne-Ambacht Midden Rechteroever Substraat", "VA_PG_LO_SU"="Veurne-Ambacht Pompgemaal Linkeroever Substraat", "VA_PG_RO_SU"="Veurne-Ambacht Pompgemaal Rechteroever Substraat", "VA_PG_LO_PA"="Veurne-Ambacht Pompgemaal Linkeroever Palinggoot", "VA_PG_RO_PA"="Veurne-Ambacht Pompgemaal Rechteroever Palinggoot", "VA_PG_KR_NA"="Veurne-Ambacht Pompgemaal Kruisnetten"))

barplot1 <- ggplot(data_inbo, aes(Location)) +
  geom_bar() +
  ggtitle("Location of glass eel catch") +
  ylab("Number of glass eel caught")
barplot1

barplot2 <- ggplot(data_inbo, aes(Catchment.method, fill  = Catchment.method)) +
  geom_bar() +
  ylab("Number of glass eel caught") +
  scale_fill_manual(values=wes_palette(n=3, name="Moonrise2")) + 
  ggtitle("Catchment method") +
  xlab(" Catchment Method")
  theme_classic()
barplot2

barplot3 <- ggplot(data_inbo, aes(month(Date), fill = month(Date))) +
  geom_bar() +
  ylab("Number of glass eel caught") +
  scale_fill_manual(values=wes_palette(n=3, name="Moonrise2")) + 
  xlab("Month of year 2017") +
  ggtitle("Month of glass eel catch") +
  theme_classic()
barplot3

pal <- wes_palette("Zissou1", 6, type = "continuous")
barplot4 <- ggplot(data_inbo, aes(week(Date), fill = ..count..)) +
  geom_bar() +
  xlab("Week of year 2017") +
  ylab("Numbers of glass eel caught") +
  ggtitle("Week of glass eel catch") +
  scale_fill_gradient(low = pal[3], high = pal[6]) +
  theme_classic()
barplot4

plot5 <- ggplot(data_inbo, aes(week(Date), length..mm.)) +
  geom_point() +
  ggtitle("Length of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method) +
  xlab("Lengte glasaal in mm") +
  ylab("Week van het jaar 2017") 
plot5

plot6 <- ggplot(data_inbo, aes(week(Date), weight.mg.)) +
  geom_point() + 
  ggtitle("Weight of glass eel vs week of catchment") +
  xlab("Gewicht glasaal in mm") +
  ylab("Week van het jaar 2017") +
  facet_grid(.~Catchment.method)
plot6

# gekke outlier eruit
data_inbo <- as.tibble(read.csv2("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Glass eel stock deepfreeze 2017.csv", sep = ";", dec = ",")) # leest de data van het inbo genoteerd bij de glasaalstaalname opnieuw, zo is datum nog geen POSIXlt object
data_inbo_wo_outlier <- filter(data_inbo, weight.mg. < 1500) # haalt er de elver uit
plot7 <- ggplot(data_inbo_wo_outlier, aes(week(Date), weight.mg.)) +
  geom_point() + 
  ggtitle("Weight of glass eel vs week of catchment") +
  ylab("Gewicht glasaal in mg") +
  xlab("Week van het jaar 2017") +
  facet_grid(.~Catchment.method)
plot7

data_inbo$Date <- strptime(as.character(data_inbo$Date), "%d/%m/%Y")

plot8 <- ggplot(data_inbo, aes(week(Date), fill = pigmentation.stage)) +
  ggtitle("Pigmentation stage of glass eel vs week of catchment") +
  geom_bar(aes(fill = pigmentation.stage), width = 1) +
  xlab("Week van het jaar 2017") +
  ylab("Aantal gevangen glasalen")
plot8


```

## Sampling location 

TO DO: map met locaties aangeduid op satellietafbeelding

VA_PG_LO_PA: Veurne Ambacht canal pumping station left bank eel ladder
VA_PG_RO_PA: Veurne Ambacht canal pumping station right bank eel ladder
VA_PG_LO_SU: Veurne Ambacht canal pumping station left bank substrates
VA_PG_RO_SU: Veurne Ambacht canal pumping station right bank substrates
VA_MI_LO_SU: Veurne Ambacht canal middle left bank substrates
VA_MI_RO_SU: Veurne Ambacht canal middle right bank substrates
VA_SC_LO_SU: Veurne Ambacht canal sluicecomplex Ganzepoot left bank substrates
VA_SC_RO_SU:  Veurne Ambacht canal sluicecomplex Ganzepoot right bank substrates
VA_PG_KR_NA: Veurne Ambacht canal pumpingstation liftnets night
GA_SU: Ganzepoot substrates

## Piecharts

https://www.zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/


```{r}

colnames <- c("Microplastics.Contaminatie.vezels..katoen..", "Cladocera.sp.", "Annelida", "Polychaete", "Isopoda", "Diptera.sp.", "Chironomida.sp.", "Crustaceae.sp.", "Cycloida.sp.", "Unidentified.sp.", 'Amphipoda.sp.', 'Calanoida.sp.', "Copepoda.sp.", "Harpacticoid.Copepod", "Hexapode.sp....", "keverlarve", "Pennate.diatomee","Plantae.sp.")

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud2, aes_string(x="''", y = colnames[i], fill = "Methode")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud2, aes_string(x="''", y = colnames[i], fill = "Locatie_A")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

```


But now, we want to constructs piecharts which are not absolute numbers, but relative numbers.
For example, if a glass eel ate 1 polychaete out of the total of 50 found polychaetes, this results in a relative number on the pie chart of 2%

```{r}
maaginhoud2 <- remove_empty(maaginhoud2, 'rows')
col_sum <- colSums(maaginhoud2[7:24], na.rm = TRUE)

maaginhoud3 <- maaginhoud2[1:6]
new_column <- list()

for (count in 7:length(maaginhoud2)) {
  new_column <- (maaginhoud2[count] / col_sum[count - 6])
  maaginhoud3 <- cbind(maaginhoud3, new_column)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud3, aes_string(x="''", y = colnames[i], fill = "Methode")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud3, aes_string(x="''", y = colnames[i], fill = "Locatie_A")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}

```

Now we want to compose relative piecharts divided according to pigmentation stage

```{r}
data_inbo_pigmentation <- data_inbo[,c("nr","pigmentation.stage")]
maaginhoud4 <- left_join(maaginhoud2, data_inbo_pigmentation, by='nr')

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud4, aes_string(x="''", y = colnames[i], fill = "pigmentation.stage")) +
    geom_bar(width = 1, stat="identity")
  pie <- bp + coord_polar("y", start= 0)
  print(pie)
}
 
```

Now we want to compare what the relative percentage caught per method & location is
To do so, we need a transposed data table. This needs some more work

```{r, eval = FALSE, echo = FALSE}
maaginhoud5 <- select(maaginhoud2, -nr, -datum, -Locatie, -Locatie_A, -Locatie_Oever)
maaginhoud5 <- group_by(maaginhoud5, "Methode")
maaginhoud5 <- data.frame(t(maaginhoud5), header = TRUE)
names(maaginhoud5) <- maaginhoud5[1,]
maaginhoud5 <- maaginhoud5[-1,]


```

## Bargraphs

Hier wordt weergegeven welke organismen op welke tijd van het jaar in verschillende pigmentatiestadia van de glasaal teruggevonden werden.

```{r}

for (i in 1:length(colnames)) {
  bp <- ggplot(maaginhoud4, aes_string(x=week(as.Date(maaginhoud4$datum)), y = colnames[i], fill = "pigmentation.stage")) +
    geom_bar(width = 1, stat="identity") +
    xlab(label = "Week of 2017")
  print(bp)
}
```

# Environmental samples

Een ideetje om de Forage ratio te berekenen. Forage ratio:

$$ \frac{percent~weight~of~food~item~i~in~stomach~of~glass~eel~w}{percent~weight~of~food~item~i~in~the~environment}~~~~ x ~~ 100  $$
Hier bekijken we eens de dataset waarin het aantal individuen per liter werd bekeken in 2016, maar om de bovenstaande ratio te berekenen zou toch een set van het jaar 2017 nodig zijn. Is die er?

```{r}
environment2016_ind <- as.tibble(read.csv("C:/Users/user/Desktop/Biologie/Master/Thesis/Thesis/data/raw/Individuals per liter 2016.csv", sep = ";", header = TRUE, dec = ","))

env_cyclo <- ggplot(environment2016_ind, aes(week(as.Date(Datum)), Cyclopoida)) +
  geom_point() +
  ylab("Cyclopoida ind/L 2016")
env_cyclo

env_alona_a <- ggplot(environment2016_ind, aes(week(Datum), Alona.affinis)) +
  geom_point() +
  ylab("Alona affinis ind/L 2016")
env_alona_a

env_alona_r <- ggplot(environment2016_ind, aes(week(Datum), Alona.rectangula)) +
  geom_point() +
  ylab("Alona rectangula ind/L 2016")
env_alona_r

env_chydorus <- ggplot(environment2016_ind, aes(week(Datum), Chydorus.sphaericus)) +
  geom_point() +
  ylab("Chydorus sphaericus ind/L 2016")
env_chydorus

env_daphnia <- ggplot(environment2016_ind, aes(week(Datum), Daphnia.galeata)) +
  geom_point() +
  ylab("Daphnia galeata ind/L 2016")
env_daphnia 

env_pleuroxus <- ggplot(environment2016_ind, aes(week(Datum), Pleuroxus.aduncus)) +
  geom_point() +
  ylab("Pleuroxus aduncus ind/L 2016")
env_pleuroxus
```




# Indices

Here, we calculate some indices from the dataset and visually explore these. 

## Stomach content analysis indices
### Condition Factor

First, the condition factor is analysed. Condition factor is already a variable in the dataset, calculated by the INBO.

Vraag voor jeroen: hoe werd deze conditiefactor juist berekend?

```{r}
plot_condfact_method <- ggplot(data_inbo, aes(week(Date), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") +
  facet_grid(.~Catchment.method) +
  xlab("Conditiefactor") +
  ylab("Week van het jaar 2017")
plot_condfact_method

plot_condfact_location <- ggplot(data_inbo, aes(week(Date), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") +
  facet_grid(.~Location)
plot_condfact_location

plot_condfact_pigm <- ggplot(data_inbo, aes(pigmentation.stage, condition.factor)) +
  geom_point() +
  ggtitle("Condition factor of glass eel vs week of catchment") 
plot_condfact_pigm

# Nu de conditiefactor duidelijker weergeven, maar nu enkel voor de al verwerkte glasalen

nr_locatie_methode <- select(maaginhoud2, nr, Locatie_A, Locatie_Oever, Methode)
nr_pigmentation_condfact <- select(data_inbo, nr, pigmentation.stage, condition.factor)

maaginhoud6 <- select(maaginhoud, nr, datum, Gewicht.Glasaal, Gewicht.maag.darmstelsel)
maaginhoud6 <- mutate(maaginhoud6, ratio_visceral_total = Gewicht.maag.darmstelsel / Gewicht.Glasaal)
maaginhoud6_wo_outlier <- filter(maaginhoud6, ratio_visceral_total < 1) # reden: zie hieronder
maaginhoud6_wo_outlier$datum <- strptime(as.character(maaginhoud6_wo_outlier$datum), "%d/%m/%Y")

maaginhoud7 <- left_join(maaginhoud6_wo_outlier, nr_locatie_methode, by='nr')
maaginhoud7 <- left_join(maaginhoud7, nr_pigmentation_condfact, by='nr')

plot_condfact_location_2 <- ggplot(maaginhoud7, aes(week(as.Date(datum)), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor vs week of catchment") +
  facet_grid(.~Locatie_A) +
  xlab("Week van het jaar 2017") +
  ylab("Conditiefactor")
plot_condfact_location_2

plot_condfact_method_2 <- ggplot(maaginhoud7, aes(week(as.Date(datum)), condition.factor)) +
  geom_point() +
  ggtitle("Condition factor vs week of catchment") +
  facet_grid(.~Methode) +
  xlab("Week van het jaar 2017") +
  ylab("Conditiefactor")
plot_condfact_method_2

```
### Number method

$$ \frac{amount~of~food~~item~i}{total~number~of~items~found~in~gut}~~~~ x ~~ 100  $$
Vertelt dit niet wat hetzelfde als de piecharts?
Onderstaande code werkt ook nog niet helemaal...

```{r, eval = FALSE}
maaginhoud_index1  <- maaginhoud2[1:6]
maaginhoud_temp <- maaginhoud2[7:24]
for (rw in 1:length(maaginhoud_temp)) { 
    tmp <- maaginhoud_temp[rw,]/sum(maaginhoud_temp[rw,]) 
    if (tmp) {
          maaginhoud_index1 <- rbind(maaginhoud_index1, tmp); 
    } else {
      maaginhoud_index1 <- rbind(maaginhoud_index1, maaginhoud_temp[rw,])
    }
} 
```


### Ratio visceral organs/total body mass

Second, we calculate the ratio of visceral organs on total body mass.Dit is een index voor de 'fulness' van de glasaal.

$$ \frac{weight~of~stomach-gut~system~of~glass~eel~w}{total~body~mass~of~glass~eel~w}~~~~ x ~~ 100  $$

```{r}
plot_ratio_method <- ggplot(maaginhoud6, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
plot_ratio_method  # Dikke outlier wegwerken

plot_ratio_method <- ggplot(maaginhoud6_wo_outlier, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
plot_ratio_method 
```

According to previous plot, glass eel do tend to be more fed at the end of spring. This is true for all catchment methods & locations. But is this really the case?

```{r}

plot_ratio_location <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Locatie_A) +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
plot_ratio_location

plot_ratio_method <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Methode) +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
plot_ratio_method

plot_ratio_location2 <- ggplot(maaginhoud7, aes(week(as.Date(datum)), ratio_visceral_total)) +
  geom_point() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs week of catchment") +
  facet_grid(.~Locatie_Oever) +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
plot_ratio_location2

plot_ratio_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Pigmentatiestadium") +
  scale_fill_manual(values=wes_palette(n=3, name="Moonrise2"))  
plot_ratio_pigm_methode

plot_ratio_pigm_locatie <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Locatie_A)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Pigmentatiestadium")
plot_ratio_pigm_locatie

plot_ratio_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  scale_fill_manual(values=wes_palette(n=3, name="Moonrise2")) + 
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs pigmentation stage") +
  facet_grid(.~Locatie_A) +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Pigmentatiestadium")
plot_ratio_pigm_methode

plot_ratio_tijd_methode <- ggplot(maaginhoud7, aes(week(datum), ratio_visceral_total, fill = Methode)) +
  geom_boxplot() +
  ggtitle("Ratio of visceral organs on total body mass of glass eel vs time") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  facet_grid(.~Locatie_A) +
  ylab("Ratio viscerale organen / Totale lichaamsgewicht glasaal") +
  xlab("Week van 2017")
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_ratio_tijd_methode

```

And indeed, it is the case across methods and locations.However, data from the pompgemaal is probably most reliable, since not all pigmentation stages were caught at other locations, and only substrates were used to catch glass eels.

## Diversity Indices

As in Charlottes' bachelorproef, we could calculate several diversity indices. However, these are clasiccally used in ecological community turnover studies. Are these really applicable?

```{r}
library(vegan)
maaginhoud_index2 <- select(maaginhoud2, nr, Microplastics.Contaminatie.vezels..katoen..:Plantae.sp.)
maaginhoud_index2 <- remove_empty(maaginhoud_index2, 'rows')


maaginhoud7 <- mutate(maaginhoud7, Shannon = diversity(maaginhoud_index2, index="shannon", MARGIN=1, base=exp(1)))
maaginhoud7 <- mutate(maaginhoud7, Simpson = diversity(maaginhoud_index2, index="simpson", MARGIN=1, base=exp(1)))

plot_Shannon_tijd_methode <- ggplot(maaginhoud7, aes(week(datum), Shannon, color = Methode)) +
  geom_point() +
  ggtitle("Shannon-Index vs time") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  facet_grid(.~Locatie_A) +
  ylab("Shannon-Index") +
  xlab("Week van 2017")
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_Shannon_tijd_methode

plot_Shannon_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, Shannon, color = Methode)) +
  geom_point() +
  ggtitle("Shannon-Index vs pigmentation stage") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  facet_grid(.~Locatie_A) +
  ylab("Shannon-Index") +
  xlab("Pigmentation Stage")
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_Shannon_pigm_methode

plot_Simpson_tijd_methode <- ggplot(maaginhoud7, aes(week(datum), Simpson, color = Methode)) +
  geom_point() +
  ggtitle("Simpson-Index vs time") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  facet_grid(.~Locatie_A) +
  ylab("Simpson-Index") +
  xlab("Week van 2017")
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_Simpson_tijd_methode

plot_Simpson_pigm_methode <- ggplot(maaginhoud7, aes(pigmentation.stage, Simpson, color = Methode)) +
  geom_point() +
  ggtitle("SImpson-Index vs pigmentation stage") +
  scale_fill_manual(values=wes_palette(n=4, name="Moonrise2")) + 
  facet_grid(.~Locatie_A) +
  ylab("Simpson-Index") +
  xlab("Pigmentation Stage")
  #facet_zoom( x = Locatie_A == "Pompgemaal")
plot_Simpson_pigm_methode
```



http://spatialecology.weebly.com/r-code--data/category/plotting

```{r, eval=FALSE}

maaginhoud8 <- select(maaginhoud2, Microplastics.Contaminatie.vezels..katoen..:Plantae.sp.)

accurve<-specaccum(maaginhoud8, method="random", permutations=100)
#plot(accurve$sites, accurve$richness, xlab="Number of glass eel analysed", ylab="Species Richness")
```


# PCA

PCA as exploration of the stomach analysis data

https://www.datacamp.com/community/tutorials/pca-analysis-r


```{r, eval = FALSE}

maaginhoud2.pca <- prcomp(na.omit(maaginhoud2[7:24]), center = TRUE, scale. = TRUE)
str(maaginhoud2.pca)
ggbiplot(maaginhoud2.pca)
```
