---
title: "Fatty Acid Analysis"
author: "Michiel Perneel"
date: "26 april 2019"
output: html_document
---

# Fatty Acid analysis

```{r setup, include=FALSE}

library(ggplot2)
library(readxl)
library(lubridate)
library(wesanderson)
library(tibble)
library(dplyr)
library(janitor)
library(plyr)
library(anytime)
library(ggforce)
library(vegan)
library(tidyr)

FA <- as.tibble(read.csv2("C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/Fatty Acids.csv", sep = ";", header = TRUE, dec = ","))

data_inbo <- as.tibble(read.csv2("C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/data_inbo_glasaal_gekuist.csv", sep = ";", header = TRUE, dec = ","))
data_inbo_sub <- filter(data_inbo, Location_type == "SU")

data_inbo2 <- as.tibble(read.csv2("C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/Glass eel stock deepfreeze 2017.csv", sep = ";", dec = ","))

```

Workflow:
- 1 multivariate & univariate approach based on the absolute concentrations (mg/g, g/100g)  
    -> If the need arises to transform the data, use double square root
  
- 1 multivariate & univariate approach based on the relative frequencies (eg. g/100g / total FA)
    -> If the need arises to transform the data, use log transformation
    -> due to homeostasy, it could very well be that this results in a patten only in frequency analysis
    
    
# --------------- Absolute Concentrations  --------------------------------
    
```{r}
temp <- select(data_inbo2, nr, Date, Catchment.method, pigmentation.stage, condition.factor)
FA_env_abs <- left_join(FA, temp, by = "nr")


FA_env_abs <- FA_env_abs %>%
  mutate(Date = as.Date(Date, format = "%d/%m/%Y"))

FA_env_abs[FA_env_abs < 0] <- NA
FA_env_abs <-FA_env_abs[complete.cases(FA_env_abs),]

write.csv(FA_env_abs[1:26], file = "C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/FA_env_abs.csv")
```

## -------------- Check assumptions ------------




# --------------- Relative Frequencies --------------------------------

```{r}
FA_env_rel <- FA_env_abs
FA_env_rel[2:26] <- FA_env_abs[2:26] / FA_env_abs$total.Fatty.acids
FA_env_rel_factors <- select(FA_env_rel, nr, Date, Catchment.method, pigmentation.stage, condition.factor)

write.csv(FA_env_rel[1:26], file = "C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/FA_env_rel.csv")

write.csv(FA_env_rel_factors, file = "C:/Users/Admin/OneDrive/Documenten/Biologie/Master/Thesis/Thesis/data/raw/FA_env_rel_factors.csv")
```



Visual Exploration

```{r}
plot1 <- ggplot(FA_env, aes(Date, total.Fatty.acids, group = Catchment.method, colour = Catchment.method)) +
  geom_point()
plot1 # elver outlier

FA_env_sub <- filter(FA_env, Catchment.method == "Substraat")

FA1 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X14.00)) +
  geom_boxplot()
FA1
FA2 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X15.00)) +
  geom_boxplot()
FA2
FA3 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X16.00)) +
  geom_boxplot()
FA3
FA4 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X16.1.iso.17.0)) +
  geom_boxplot()
FA4
FA5 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$cis.9.16.1)) +
  geom_boxplot()
FA5
FA6 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X17.00)) +
  geom_boxplot()
FA6
FA7 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X17.1.16.2)) +
  geom_boxplot()
FA7
FA8 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X18.00)) +
  geom_boxplot()
FA8
FA9 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$cis.9.18.1)) +
  geom_boxplot()
FA9
FA10 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$cis.11.18.1)) +
  geom_boxplot()
FA10
FA11 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X18.2n.6)) +
  geom_boxplot()
FA11
FA12 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.00)) +
  geom_boxplot()
FA12
FA13 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X18.3n.3)) +
  geom_boxplot()
FA13
FA14 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X18.4n.3)) +
  geom_boxplot()
FA14
FA15 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.01)) +
  geom_boxplot()
FA15
FA16 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.3n.6)) +
  geom_boxplot()
FA16
FA17 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X22.00)) +
  geom_boxplot()
FA17
FA18 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.4n.6)) +
  geom_boxplot()
FA18
FA19 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.4n.3)) +
  geom_boxplot()
FA19
FA20 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X20.5n.3)) +
  geom_boxplot()
FA20
FA21 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X24.01.00)) +
  geom_boxplot()
FA21
FA22 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X22.5n.6)) +
  geom_boxplot()
FA22
FA23 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X22.5n.3)) +
  geom_boxplot()
FA23
FA24 <- ggplot(FA_env_sub, aes(as.character(week(Date)), FA_env_sub$X22.6n.3)) +
  geom_boxplot()
FA24



```

Correlations

```{r}
total_condition <- ggplot(FA_env_sub, aes(total.Fatty.acids, condition.factor)) +
  geom_point()
total_condition

total_pigm <- ggplot(FA_env_sub, aes(Date, total.Fatty.acids, group = pigmentation.stage, colour = pigmentation.stage)) +
  geom_point()
total_pigm
```

